Convex Surrogates via Polyhedral Losses

### 2019-04-24 neurips-19/cvx-fin.tex
Added folder for neurips submission

\documentclass[anon,12pt]{colt2019}
\usepackage[utf8]{inputenc}
\usepackage{mathtools, amsmath, amssymb, graphicx, verbatim}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
\usepackage{color}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}

@@

%\newtheorem{theorem}{Theorem}
%\newtheorem{lemma}{Lemma}
%\newtheorem{proposition}{Proposition}
%\newtheorem{definition}{Definition}
%\newtheorem{corollary}{Corollary}
%\newtheorem{conjecture}{Conjecture}

\title{Convex Surrogates via Polyhedral Losses}
\coltauthor{%
 \Name{Jessie} \Email{email}\\
 \addr CU
 \AND
 \Name{Raf} \Email{email}\\
 \addr CU
 \AND
 \Name{Bo}  \Email{email}\\
 \addr MSFT
}

@@

\begin{keywords}%
  information elicitation, proper scoring rules, surrogate loss functions
\end{keywords}

@@

Convex surrogates have been formalized and investigated in a variety of past work such as \citet{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification}, particularly in the context of $0-1$ loss, distributions on just two outcomes, and support vector machines.

@@

\section{Higher-Dimensional Embeddings}\label{sec:general-dimensions}

Orderability is a useful characterization of 1-embeddable properties, in the sense that the orderability of a property is easily tested.
We seek a similar condition for higher dimensions.
Toward this end, let us decompose orderability into two conditions which will lend themselves to generalization.
A property $\gamma$ is orderable if and only if there exist closed intervals $[a(r)_y,b(r)_y] \subseteq \reals$ for all $r\in\R, y\in\Y$, such that the following two conditions hold:
\begin{enumerate}\setlength{\itemsep}{0pt}
\item (Optimality) For all $r\in\R, p\in\simplex$, we have $r\in \gamma(p) \iff \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p}$.
\item (Monotonicity) There exists an ordering $\R=\{r_1,\ldots,r_k\}$ such that for all $y\in\Y$, $i\in\{1,\ldots,k-1\}$, we have $b(r_i) = a(r_{i+1})$.
\end{enumerate}
Thinking of the intervals $[a(r)_y,b(r)_y]$ as subgradients of a convex function $L_y$, the first condition states that the report $r$ is optimal exactly when it should be, and the second states that the intervals are indeed subgradients of some convex function.

Generalizing the above to higher dimensions, we obtain the following.
\begin{theorem} \label{thm:char}
  A finite property $\gamma:\simplex\toto\R$ is $d$-embeddable if and only if there exist polytopes $T(r,y) \subseteq \reals^d$ for all $r\in\R, y\in\Y$, such that the following two conditions hold:
  \begin{enumerate}\setlength{\itemsep}{0pt}
  \item (Optimality) For all $r\in\R, p\in\simplex$, we have $r\in \gamma(p) \iff 0 \in \sum_{y\in\Y} p_y T(r,y)$, where summation is the Minkowski sum.
  \item (Monotonicity) There exists an embedding $\varphi: \R \to \reals^d$ and set of convex functions $\{L_y:\reals^d\to\reals\}_{y\in\Y}$ such that for all $y\in\Y, r\in\R$ we have $T(r,y) = \partial L_y(\varphi(r))$.
  \end{enumerate}
\end{theorem}

%\bo{Added the below blurb}
%\raf{I love it.  This would be a great place to discuss the relationship to FSD, which is ``even more local'' in the sense that it does not even look at a whole cell at once, just one piece of the boundary.  We can then say that the additional power is strong enough to give novel lower bounds where FSD remains silent.  (In particular, abstain looks 1d / orderable when zoomed in as far as FSD, but one can conclude it is not orderable using condition 1 alone.)}
This characterization decomposes embeddability into \emph{local} and \emph{global} necessary and sufficient conditions.
The local conditions at each embedding point turn out to imply very strong restrictions on the structure of possible polyhedral losses, regardless of any other structure in the property or where the embedding points are placed.
Meanwhile, the global condition says that, once each local embedding point's demands are satisfied, we must be able to place them all in $\reals^d$ in a coherent manner that simultaneously respects all of their requirements.

For one-dimensional embeddings, the monotonicity property is extremely useful for lower bounds, as it is easy to check whether or not a given property is orderable.
\jessiet{Replace ''However'' with some other filler?}
However, for higher dimensions, we suggest that the optimality condition is also a promising direction for lower bounds.
To that end, we next derive a more specific necessary condition and use it to prove a lower bound on the ``abstain loss''.

%\bo{I think we should write separately the result that the expected loss function only has vertices above the embedding points (um, sort of - WLOG?). I think we've known it for so long we forgot that it's a really interesting and also a necessary and sufficient condition. Does it also imply that each individual loss function's vertices can only be at embedding points?}
%\raf{This is one of those statements that is probably true in some sense but we're not sure what sense.  There could be vertices that are just never optimal, and it's hard to know exactly how to rule them out.}

\subsection{Necessary condition: $d$-construction}

Each embedding point's optimality condition turns out to imply limitations on \emph{each} of the $n$ loss functions.
This can be enough to rule out embeddability only by considering a single level set, as we develop next.

Recall that a \emph{halfspace-representation (H-rep)} of a closed polyhedral set $T$ in $d$ dimensions is a pair $(V,b)$ with $V \in \reals^{k \times d}$ and $b \in \reals^k$ such that $T = \{ w : Vw \leq b \}$.
We say an H-rep is \emph{tight} if for all $i=1,\dots,k$, there exists $w \in T$ such that $\langle V_i , w \rangle = b_i$.

\begin{definition}\label{def:d-construction}
  Given a polytope $\{p \in \Delta_{\Y} : Bp \geq 0\}$ for $B \in \reals^{k \times n}$, a \emph{$d$-construction} of it is a $V \in \reals^{k \times d}$ such that, for each column $B_i$ of $B$, the pair $(V,B_i)$ is a tight halfspace representation.
  \jessiet{Should we mention the known results that elicitable properties have convex level sets, and such a convex polytope exists (and in fact describes the level set) before the definition?}
\end{definition}

\begin{corollary}\label{cor:d-embed-implies-d-construction}
  If a property is $d$-embeddable, then each of its level sets has a $d$-construction.
\end{corollary}

This provides the following recipe for both constructing losses and proving lower bounds.
First, take any level set and represent it as $\{p : Bp \geq 0\}$.
\jessiet{Is there any reason why $p \in \simplex$ would be implicit and not be required in $B$?  Asking more for the }
Now if $B$ has $k$ rows, search for a collection of $k$ vectors in $\reals^d$.
For any candidate $V$ (whose rows are the vectors), a computer program can automatically verify whether the representations $\{(V,B_y)\}_{y \in \Y}$ are tight.
In particular, if any $(V,B_y)$ is infeasible (i.e. there does not exist any $w$ satisfying all constraints $\langle v_i, w \rangle \leq B_{iy}$), then $V$ is not a $d$-construction.
If $(V,B_y)$ is feasible but some constraints are redundant, i.e. it is not tight, then again we do not have a $d$-construction.

If a $d$-construction $V$ is found, one also obtains that the subgradient sets $\partial L(u)_y$ must ``span'' the respective polytopes $\{w : Vw \leq B_y\}$, i.e. must be contained within them and must make each constraint tight.
Repeating this process for each level set and associated embedding point gives a relatively tight picture of what any possible loss must look like.

A lower bound can be proven by showing, for any level set, that no collection of $k$ vectors can form a $d$-construction.
We will give examples of this in $2$ dimensions next.

\paragraph{Other necessary conditions.}
One can also derive other kinds of potentially necessary conditions from the general characterization in Theorem \ref{thm:char}.
One is related to the weak monotonicity property of convex functions.\bo{raf please fill in}
Another is a reduction to the one-dimensional characterization. If one considers any embedded property in $\reals^d$ and restricts the report space to a line while keeping the loss the same, one obtains a new $1$-dimensional embedded property.
\jessiet{Does the original property refine of the restricted property?  If so, that might be worth mentioning.}
Picking a line that e.g. goes through previous embedding or indifference points, those that were optimal originally must still be optimal under the same distribution.
At this point, the one-dimensional characterization may rule out embeddability.

\subsection{Example}
We give an example of how this necessary condition can be applied to prove a lower bound.
\jessiet{Throughout: find/replace 0.5 with 1/2.}
The \emph{abstain property} sets a threshold of $\alpha$ (here, $\alpha=0.5$) and has $\R = \Y \cup \{\text{abstain}\}$.
We have $\text{abstain} \in \gamma(p) \iff \max_y p_y \leq \alpha$, and $y \in \gamma(p) \iff p_y = \max_{y'} p_{y'}, p_y \geq \alpha$.
In other words, it is similar to the mode, except that if none of the options has a high enough probability, the best report is to abstain.
\jessiet{Would it be helpful to have drawings of the [3-outcome] simplex for abstain(1/2) and mode to see the difference?}
\citet{ramaswamy2018consistent} show that this property on $|\Y|=n$ can be embedded in $\lceil \log_2(n) \rceil$ dimensions.
Their construction is quite beautiful and extremely instructive for studying embeddings.
In particular, it shows how to embed abstain$(0.5)$ on $4$ outcomes into $\reals^2$.
Prior to this work, it was not known if one could improve by embedding abstain($0.5$) for $5$ or more outcomes in $\reals^2$.

%\begin{theorem}[\bo{cite}]
%  \bo{Still not proven}
%  The mode with $|\Y|=n$ is not $(n-2)$-embeddable.
%\end{theorem}
%\begin{proof}
%  Call the outcomes $\Y = \{1,\dots,n\} = \R$.
%  We will pick the level set for the report $r=n$ and show it has no $d$-construction.
%  There are two kinds of constraints on the level set.
%  The constraints that $n$ be the mode implies $p_n \geq p_i ~ (\forall i \neq n)$.
%  These can be rearranged as $-p_i + p_n \geq 0$.
%  Then there are nonnegativity constraints on each $p_i$.
%  This is redundant for $p_n$ so cannot be included.
%  \[ B = \begin{pmatrix}
%        -1 &  0 & \cdots & 0  & 1 \\
%         0 & -1 & \cdots & 0  & 1 \\
%           &    & \vdots &    &   \\
%         0 &  0 & \cdots & -1 & 1  \\
%         \hline
%         1 &  0 & \cdots &    & 0  \\
%         0 &  1 & \cdots &    & 0  \\
%           &    & \vdots &    &    \\
%         0 &    &        & 1  & 0
%     \end{pmatrix} .
%  \]
%  Here $B$ has $2(n-1)$ rows, which we will call $1,2,\dots,n-1,1',2',\dots,(n-1)'$.
%
%  A $d$-construction is therefore a $V$ with $n-1$ rows, each a vector $v_i$ in $\reals^d$.
%  Suppose $d \leq n-2$, i.e. there are at least $d+1$ rows.
%  Now consider the halfspace representation given by the second column of $B$, namely $T = \{ w : Vw \leq (-1, 0, \dots, 0)^{\intercal}\}$.
%  The first $d+1$ rows are linearly dependent in $\reals^d$.
%  Therefore, we can write the $d+1$st row as $v_{d+1} = \alpha_1 v_1 + \cdots + \alpha_d v_d$.
%  So if $w \in T$, then $\inprod{v_1}{w} \leq -1$ and $\inprod{v_i}{w} \leq 0$ for all $i=2,\dots,d$.
%  Taking the weighted combination, we obtain $\inprod{v_{d+1}}{w} \leq -\alpha_1$.
%  If $\alpha_1$ is positive, this implies there is slack in the $d+1$st constraint, so the halfspace representation cannot be tight.
%  If $\alpha_1$ is nonpositive, then we pick some other pair of vectors $i \neq j$ rather than $1,d+1$, such that $v_j = \sum_{i'\neq j} \alpha_{i'} v_{i'}$ with $\alpha_i > 0$.
%  \bo{I claim there must exist two such vectors in this collection ... need to prove it though!}
%  Choosing the $i$th column of $B$ as a constraint gives the contradiction as above.
%\end{proof}

\begin{theorem}\label{thm:abs-5outcome-not-2embed}
  Abstain with $\alpha=1/2$ and $|\Y|=5$ is not $2$-embeddable.
\end{theorem}

%%%% Previous versions of proofs:
%In fact, in order for the H-reps to be tight, we must observe that for all $i, j$, the $\max_{x \in S_i} \langle v_j, x \rangle = -1$ if $i = j$ and $1$ otherwise.
%For all $i,j$, we denote $x_{ij}$ so that $\langle v_i, x_{ij} \rangle = \langle v_j, x_{ij} \rangle = 1$.
%Numbering the normals clockwise (modulo 5), then for all $i$, we need $\langle v_i, x_{i+1, i+2} \rangle \leq -1$ and $\langle v_i, x_{i-1, i-2} \rangle \leq -1$.
%
%Focusing on $v_1$, we know that $\langle v_1, x_{23} \rangle \leq -1$ and $\langle v_1, x_{45} \rangle \leq -1$ if and only if $\theta_{13} = \theta_{12} + \theta_{23} \geq 180^o$  and $\theta_{41} = \theta_{51} + \theta_{45} \geq 180^o$.
%These statements are only jointly true if $\theta_{13} = \theta_{41} = 180^o$.
%However, the only way to reach this conclusion is if $\theta_{34} = 0^o$, and as the vectors are all unit vectors, we conclude $v_3 = v_4$.
%We can see that this scenario contradicts the tightness of the H-reps $(V, B_3)$ and $(V, B_4)$.
%As $S_3 = \{w : Vw \leq (1,1,-1,1,1)^T\}$, if $v_3 = v_4$, then the polytope $S_3$ is a line in $\reals^2$ and the constraint $\langle v_1, x \rangle = 1$ is not true for any $x \in S_3$.
%Therefore, there is some $i$ such that $(V,S_i)$ is not a tight H-representation.
%Thus, the cell $B^{(abs)}$ does not have a $2$-construction, and the property is not $2$-embeddable.

%Similarly, we can see that $\langle v_2, x_{34} \leq -1$ and $\langle v_2, x_{15} \rangle \leq -1$ if and only if $v_4 = -v_2$.
%Therefore, we know that $\theta_{24} = 180^o = \theta_{23} + \theta_{34} = \theta_{12} + \theta{51} + \theta_{45}$
%
%Now, in order for $\langle v_5, x_{12} \leq -1$ and $\langle v_2, x_{34} \rangle \leq -1$ to hold,
%
%Therefore, for all $v_i$, there must be some $v_j = -v_i$ in $V$.
%
%Consider $V = (v_1, \ldots, v_5)^T$ and, without loss of generality, let $v_1 = (0,1)$.
%
%
%We assert that $v_2 := -v_1$ must be in the set of normals.
%This can be seen since, for the normals $v_1$ and $v_2$, then angle $\theta_{12}$ between the two normals must be $180^o$.
%Since we have $5$ normals, the angle between normals $v_1$ and $v_2$ can be written $\theta{12} = \theta{1i} + \theta_{i2}$.
%(One direction of the angles must have some $v_i$ between $v_1$ and $v_2$.)
%If $\theta_{1i} \leq 90^o$, then $\theta_{1i} + \theta_{i2} \geq 180^o$ in order for there to be a $w$ such that $\langle v_2, w \rangle = 1$.
%
%
%\jessie{Left off here before the reading group}
%In order for the H-rep to be tight, then for all $v_j$ for $j > 1$, $\langle v_j, w \rangle = 1$ and $w = (x, -1)$.
%Observe that a line (here, a facet of the polytope) in $\reals^2$ cannot be non-redundantly bounded by $3$ points.
%This suggests that, in order for $(V,B_1)$ to be tight, at least two facets must both intersect $\langle v_1, w \rangle$ at the same point.
%However, since each $v_j$ must be a unit normal and the facets must intersect at the same point $w$, $\langle v_j, w \rangle = \langle v_k, w \rangle$ for $j \neq k$ if and only if $v_j = v_k$.
%However, if $v_j = v_k$, then the representations $(V, B_j)$ and $(V, B_k)$ will not be tight.
%This can be seen as there will be no $w \in \{ w: \langle v_j, w \rangle = 1 \}$ that is also on the face $\{w : \langle v_j, w \rangle =-1 \} = \{w : \langle v_k, w \rangle = -1\}$, and vice versa.
%Therefore, there is no set of normals $V \in \reals^{5\times 2}$ so that $\{w : Vw = B_i\}$ is tight for all $v_j$ and $B_i$.
%Therefore, since there is no $2$-construction of abstain(1/2) on $5$ outcomes, we conclude it is not $2$-embeddable.
%\jessie{Weird to think of it this way after drawing so many pictures, but this might be more elegant if it's close.}

\paragraph{On the matching upper bound.}
One cannot prove a better lower bound for abstain loss and $\reals^2$, as \citet{ramaswamy2018consistent} give a $2$-embedding for $|\Y|=4$.
This implies that a $2$-construction for the $4 \times 4$ version of the above $B$ matrix exists; and indeed, the above proof roughly reveals its shape.
One can take $V$ to be the four unit vectors pointing directly north, south, east, and west; the H-representations are then line segments, e.g. the segment $w_1=-1, w_2 \in [-1,1]$, etc.
These are all tight.
Indeed, as required by our characterization, the subgradient sets of their loss functions at the abstain embedding point span these H-reps (in fact are equal to them).

\bo{It would be nice to actually construct the losses for the ``rhombus'' and show that it embeds abstain loss. That might be a cool showcase for our understanding.}

\begin{theorem}\label{thm:abstain-alphaghalf-not-2e}
  Abstain with $\alpha > 1/2$ and $|\Y|=6$ is not $2$-embeddable.
\end{theorem}

\paragraph{Implications.}
We conjecture that the construction of \citet{ramaswamy2018consistent} is optimal in all dimensions.
If so, this leaves two possibilities: It might be that there is some \emph{non-embedding} approach that elicits this property using a report space of fewer than $d=\lceil \log_2 |\Y|\rceil$ dimensions.
Going beyond the embedding approach seems to require new ideas that could be relevant to many applications in machine learning.
On the other hand, it might be that the best possible dimension is achieved by an embedding approach and polyhedral loss.
If true, it would be interesting to see how generally this might hold.
\begin{conjecture}\label{conj:abstain-tight}
  Abstain with $\alpha=1/2$ is $(\log_2 |\Y|)$-embeddable, but no lower.
  \jessiet{Add the ceil macros}
\end{conjecture}

@@

\raf{ACKNOWLEDGEMENTS (commented out for submission)}
% \subsection*{Acknowledgements}
% We thank Peter Bartlett for several discussions early on, which led to a proof of \raf{1-d reduction} among other insights.
% \raf{Almost forgot: should ack Arpit too of course!}

\bibliography{diss,extra}

@@

%\end{proof}

\section{To Sort}
\jessiet{Lol we should probably change the name of this}
Several definitions from \citet{aurenhammer1987power}.
\begin{definition}\label{def:cell-complex}
  A \emph{cell complex} in $\reals^d$ is a set $C$ of faces (of dimension $0,\ldots,d$) which (i) union to $\reals^d$, (ii) have pairwise disjoint relative interiors, and (iii) any nonempty intersection of faces $F,F'$ in $C$ is a face of $F$ and $F'$ and an element of $C$.
\end{definition}

@@

\section{Higher dimensions}
\begin{proof}[Proof of Corollary~\ref{cor:d-embed-implies-d-construction}]
  Suppose the level set is represented as $\Gamma_r = \{p : Bp \geq 0\}$ with $B \in \reals^{k \times n}$ for the minimum $k$ (i.e. the number of facets of the polytope).
  Let $u \in \reals^d$ be its embedding point.
  The convex expected loss is minimized at $u$ if and only if it has the zero vector as a subgradient at $u$, i.e.
    \[ p \in \Gamma_r \qquad \iff \qquad 0 \in \partial \langle L(u), p \rangle . \]
  Subgradient sets satisfy the following two properties: $\partial(f_1 + f_2) = \partial f_1 + \partial f_2$ where the right side is the Minkowski sum of the subgradient sets (i.e. the set of sums of all pairs); and $\partial(\alpha f_1) = \alpha \partial f_1$.
  So
    \[ \partial \langle p , L(u) \rangle = \sum_{y \in \Y} p_y \partial L(u)_y \]
  where the right side is a Minkowski sum of subgradient sets.
  We now consider the halfspaces defining this set.
  Define the $y$th support function as $H_y(v) = \max_{w \in \partial L(u)_y} \langle w, v \rangle$ to obtain that $w \in \partial \langle p, L(u) \rangle$ if and only if, for all unit vectors $v$, \jessiet{Do the vectors have to be unit vectors?}
   \[ \langle v, w \rangle \leq \sum_{y \in \Y} p_y H_y(v) . \]
  In particular, the embedding point is optimal for $p$ if and only if this is satisfied for $w=0$.
  \jessiet{... be the $i$th column of $B$, as given in Definition 24...}
  So, letting $B_i$ be the $i$th column of $B$, we have
    \[ \Gamma_r = \{p : \sum_y p_y B_y \geq 0\} = \{p : \sum_y p_y H_y(v) \geq 0 ~ (\forall v, \|v\|=1)\} . \]
  These sets are equal and full-dimensional as polytopes.
  By standard results (e.g.~\cite{grunbaum2013convex}), their H-representations are unique, so we must have $k$ vectors $v_1,\dots,v_k \in \reals^d$ such that $H_y(v_i) = B_{iy}$.
  Collected as rows of $V$, we obtain that each $(V,B_y)$ is a tight halfspace representation, as it contains $\partial L(u)_y$ and $H_y(v_i) = B_{iy}$, meaning there exists $w \in \partial L(u)_y$ such that $\langle w, v_i \rangle = B_{iy}$.
  \jessiet{For this proof, do we want to use a variable besides $w$ since it is used earlier in the inequality $\inprod{v}{w} \leq \sum p_y H_y(v)$?}
\end{proof}

\bo{A whole section of the following proof can be cut out, but it's trying to be a tutorial. Pairs well with the figure}
\begin{proof}[Proof of Theorem~\ref{thm:abs-5outcome-not-2embed}]
By Corollary~\ref{cor:d-embed-implies-d-construction}, we can show there is no $2$-construction for one of the level sets.
We choose the abstain cell, which is $\{p : \max_y p_y \leq 0.5\}$.
Because this equals $\{p : (\forall y) 2p_y \geq \sum_{y'} p_{y'}$\} \jessiet{$\sum_{y' \neq y} p_{y'}$?}, we can write the level set as $\{p : Bp \geq 0\}$ for
  \[ B = \begin{pmatrix}
       -1 &  1 &  1 & \cdots & 1  \\
       1  & -1 &  1 & \cdots & 1  \\
          &    &    & \vdots &    \\
       1  &  1 &  1 & \cdots & -1
     \end{pmatrix} .
  \]
In other words, $B := \ones - 2I$, where $\ones$ is the all-ones matrix and $I$ is the identity.
\jessiet{Do we need a different symbol for the ones matrix since $\ones$ is typically used for the vector?  We could also write $\ones \ones^T$}
In our example, $|\Y| = 5$, so $B$ has width $5$ because there are $5$ outcomes and height $5$ because there are $5$ constraints (one per outcome).

We then want to show there is no $V\in \reals^{5\times 2}$ so that for all $i \in \{1, 2, \ldots, 5\}$, $(V, B_i)$ is a tight H-rep, following Definition~\ref{def:d-construction}.
%Therefore, we show that there is no $V \in \reals^{5 \times 2}$ such that $S_i := \{w : Vw \leq B_i \}$ is nonempty and for $j = 1, \ldots, 5$, there is a $x \in \reals^2$ such that $\langle v_j, x \rangle = B_{ij}$.

Geometrically, a $2$-construction consists of $5$ vectors in the plane. (There are $5$ because there are $5$ rows of $B$.)
Once we place these vectors (picture e.g. the regular pentagon), for each column $B_y$ of $B$, we create a polytope $T_y = \{w : Vw \leq B_y\}$.
Here each vector $v_i$ gives us the halfspace $\inprod{v_i}{w} \leq B_{iy}$.
For example, if the column $B_y = (1,1,1,1,1)^{\intercal}$, then these constraints are all of the form $\inprod{v_i}{w} \leq 1$ and $T_y$ would be the regular pentagon (where the vectors are at the midpoints of each side).
In this case, $B_y$ has a single $-1$, so we get the regular pentagon but cut off from one side, leaving a triangle.
We can see in this case that some constraints are strictly redundant; the halfspaces $\inprod{v_i}{w} \leq 1$ do not all support this triangle.
Therefore, the H-rep $(V,B_y)$ is not tight.
So the regular pentagon cannot be a $2$-construction of $B$.

In the remainder of the proof, we extend the above to show that no configuration of $5$ vectors produces a tight $2$-construction.

Let $v_1,\dots,v_5$ be any $5$ different vectors in $\reals^2$, rows of a matrix $V$.
Let $T_y = \{w : Vw \leq B_y\}$ for each column $B_y$ of $B$, $y\in\{1,\dots,5\}$.
Recall we wish to prove that not all H-reps $(V,B_y)$ are tight, or in other words, there is some strictly loose constraint in one of the definitions of $T_y$.

WLOG, suppose $v_1 = (0,1)$ and they are numbered clockwise with $\|v_1\| \geq \|v_j\| (\forall j \neq i)$.
Let $\theta_{i,j}$ be the clockwise angle between $v_i$ and $v_j$.
The vectors point to the sides of an irregular pentagon $T^* = \{w : Vw \leq \vec{1}\}$.
Let $w_{1,2}$ be the corner of this pentagon between $v_1$ and $v_2$, and so on.
In our case, each $T_y$ is the intersection of $T^*$ with a halfspace, $T_y = \{w \in T^* : \inprod{v_y}{w} \leq -1\}$.
So in particular, $(V,B_1)$ is tight only if all three vertices $w_{23},w_{34},w_{45}$ satisfy $\inprod{v_1}{w} \leq -1$.
(If for example $\inprod{v_1}{w_{23}} > -1$, then the constraint $\inprod{v_2}{w} \leq 1$ is not tight, i.e. there is a separation between it and $T_1$.)
Because $v_1$ is the largest vector by assumption, this implies $\theta_{13} \geq 180^{\circ}$, but it also implies $\theta_{41} \geq 180^{\circ}$, which is a contradiction (both vectors would have to lie directly opposite $v_1$, but then they would be equal).
\jessiet{Equal or a  nonnegative scalar multiple of each other, in which case, we have a redundant constraint.}
\jessiet{Fix label for $T_5$ on image}
\begin{center}
\begin{tikzpicture}[scale=2.0]
 \path[fill=gray, opacity=0.2] (0.95105651629,0.30901699437) coordinate(p1) --  ++(180:1) coordinate(p5)
 -- ++(252:1) coordinate(p4) --
 ++(324:1) coordinate(p3) --  ++(396:1) coordinate(p2);

 \coordinate (ctr) at (barycentric cs:p1=1,p2=1,p3=1,p4=1,p5=1);
 \foreach \X [count=\Y] in {2,...,6}
 {\ifnum\X=6
   \path (p\Y) -- (p1) coordinate[pos=0.0](a\Y) coordinate[pos=1.0](a1)
   coordinate[pos=0.5](m1);
   \draw (a\Y) -- (a1);
   \draw[-latex] (ctr) -- ($ (m1)!0.0cm!90:(p1) $) node[pos=1.2]{$v_{\Y}$};
  \else
   \path (p\Y) -- (p\X) coordinate[pos=0.0](a\Y) coordinate[pos=1.0](a\X)
   coordinate[pos=0.5](m\X);
   \draw (a\Y) -- (a\X);
   \draw[-latex] (ctr) -- ($ (m\X)!0.0cm!90:(p\X) $) node[pos=1.2]{$v_{\Y}$};
  \fi}
  \draw[fill=blue, opacity = 0.2] (-1.0,-0.95105) -- (-1.0,-1.52) -- (2.0,-1.52) -- (2.0,-0.95105) -- cycle;
  \node[rotate=54, xshift=0.5cm] at (ctr) {\tiny$\theta_{5,1}$};
  \draw (0.555, -0.35) arc (18:90:0.12);
  \node at (0.5,-1.32) {\tiny$T_5 := \{w : \langle v_5, w\rangle \leq -1 \}$};
  \draw[fill=blue, opacity = 0.8] (m3) -- (m4) -- (a3) -- cycle;
\end{tikzpicture}
\end{center}
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:abstain-alphaghalf-not-2e}]
  Like Theorem~\ref{thm:abs-5outcome-not-2embed}, we will again show that there is no $2$-construction of the abstain cell.
  We then write the matrix $B$ describing the abstain cell as follows:
	\[ B = \begin{pmatrix}
       -\beta &  1 &  1 & \cdots & 1  \\
       1  & -\beta &  1 & \cdots & 1  \\
          &    &    & \vdots &    \\
       1  &  1 &  1 & \cdots & -\beta
     \end{pmatrix} .
  \]

  We know that $\beta := 1 - \frac{1}{1-\alpha} \in (0,1)$ as the inequalities describing $\alpha$ are strict.
  Observe that for all $i \in \{1,2, \ldots, 6\}, ||v_i|| > 0$. \jessiet{Give a reason.}
  Additionally, we know $-\beta < 0$.
  Therefore, for all $i$, we know that $0 \not \in T_i$.
  \jessiet{Elaborate}
  By convexity of $T_i$ for all $i$, we then know that there is no line containing the origin in $T_i$.
  WLOG, as before, we say $v_1 = (0,1)$ and $||v_1|| \geq ||v_j||$ for all $j \neq 1$, we know that $\vec{0} \not \in T_1$.

  \jessiet{Chance $o$ to $\circ$ for degrees}
  We assert that, in order for $(V, T_1)$ to be tight, then for all $j \neq i$, there must be a $w \in T_1$ such that $\inprod{v_j}{w} = 1$.
  However, in order for that to be true, $\theta_{1,j} > 60^o$. for all $j \neq 1$.
  Namely, $\theta_{1,2} > 60^o$, and $\theta_{6,1} > 60^o$.
  Observe that this argument is similar to the argument of Theorem~\ref{thm:abs-5outcome-not-2embed}.
  \jessiet{cut the first ``argument''}

  Applying the same argument iteratively, we know that if $v_c$ is the second-longest normal, in order for $(V, T_c)$ to be tight, we must observe $\theta_{c-1, c} > 60^o$ and $\theta_{c,c+1} > 60^o$.
  In fact, this argument must hold for each $\theta_j, j+1$.
  \jessiet{Fix typo above}
  Additionally, we see for all $j$, that $\theta_{j,j+2} > 120^o$.
  However, since we know $\sum_{i=1}^6 \theta_{i,i+2} = 720$, and thus there must be some $\theta_{i,i+2} \leq 120$, yielding a contradiction.

  For the normals $v_i$ and $v_{i+2}$ such that $\theta_{i,i+2} \leq 120^o$, there is no way for the H-representation $(V, T_{i+1})$ to be tight. \jessie{justify...}

  Therefore, there is no $V$ yielding a $2$-construction for abstain on $6$ outcomes with $\alpha > 1/2$.
  (Like the triangle observed in the previous proof, we observe that, on the regular hexagon, $T_1$ is a trapezoid with some constraints that are not tight.)
  \jessiet{Add in tikz graphic for this image as well.}
\end{proof}

>>>>

\documentclass[12pt]{article}
\usepackage[preprint]{neurips_2019}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage[implicit=false, bookmarks=false]{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\usepackage{mathtools, amsmath, amssymb, amsthm, graphicx, verbatim}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
\usepackage{color}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}

@@

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{conjecture}{Conjecture}

\title{Convex Surrogates via Polyhedral Losses}
\author{%
 Jessica Finocchiaro \\
 \texttt{jefi8453@colorado.edu}\\
 CU Boulder
 \And
 Rafael Frongillo\\
 \texttt{raf@colorado.edu}\\
 CU Boulder
 \And
 Bo\\
 \texttt{bwag@colorado.edu}\\
 MSFT
}

@@

%\begin{keywords}%
%  information elicitation, proper scoring rules, surrogate loss functions
%\end{keywords}

@@

Convex surrogates have been formalized and investigated in a variety of past work such as \cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification}, particularly in the context of $0-1$ loss, distributions on just two outcomes, and support vector machines.

@@

@@

\raf{ACKNOWLEDGEMENTS (commented out for submission)}
% \subsection*{Acknowledgements}
% We thank Peter Bartlett for several discussions early on, which led to a proof of \raf{1-d reduction} among other insights.
% \raf{Almost forgot: should ack Arpit too of course!}
\bibliographystyle{plainnat}
\bibliography{diss,extra}

@@

%\end{proof}
\newpage
\section{To Sort}
\jessiet{Lol we should probably change the name of this}
Several definitions from \citet{aurenhammer1987power}.
\begin{definition}\label{def:cell-complex}
  A \emph{cell complex} in $\reals^d$ is a set $C$ of faces (of dimension $0,\ldots,d$) which (i) union to $\reals^d$, (ii) have pairwise disjoint relative interiors, and (iii) any nonempty intersection of faces $F,F'$ in $C$ is a face of $F$ and $F'$ and an element of $C$.
\end{definition}

@@
